Static contract checking for Haskell

### 2011-12-21 paper/paper.tex
Paper: updated '[| e ::: CF |]v' per experiments.

 -- Need 'min(e)' here to unfold defs.
[[e in cf]]+ := min(e) ->  cf(e)
[[e in cf]]- := cf(e)

>>>>

-- Need 'min(e)' here in the (+)-case to unfold defs.
-- The 'min(e)' in the (-)-case doesn't seem strictly
-- necessary, but it gives a big performance improvement for
-- 'yes/add-symmetric.hs', from 48s to 30s for a full check.
[[e in cf]]v := min(e) ->  cf(e)
